\section{Background and Motivation}
\label{sec:background}
In this section, we discuss our motivation for designing \Sys and give the necessary background on Bitcoin needed to understand \Sys's design.

\subsection{Motivation}
\label{sec:background:motivation}
Our main motivation for designing \Sys is to provide proactive security to many applications that depend on it.
At the same time, we want to improve previous blockchain-based transparency schemes\cite{keybase,virtualchain} whose shortcomings we describe in \secref{sec:background:motivation:blockchain-transparency}.
Finally, we want a non-equivocation scheme that does not require many trustworthy parties to come into existence and that can be deployed today.

\subsubsection{Key Transparency}
\label{sec:background:motivation:key-transparency}
% NOTE: Under their threat models (e.g., gossip works), they also prevent equivocation.
% .ECT: Section 2.2, page 3
% .DTKI: Section 6, page 12
% .CONIKS: Section 2.1, "Auditors", page 4
% .AKI: 
%   Section 4, page 3, Figure 1: browsers check roots against validators.
%   Section 2.2, page 2: non-collusion between CAs, log servers and validators. EFF is a validator.
% .ARPKI:
%   Section 4, page 4: Non-equivocation? (security) still holds even when n - 1 entities are compromised. Validators are optional (CAs are validators).
\Sys can prevent equivocation attacks in current key transparency work\cite{ct,ect,dtki,arpki,aki,coniks} and, as a result, thwart man-in-the-middle (MITM) attacks.
Key transparency schemes bundle public key bindings together into a directory implemented using authenticated data structures\cite{ad}.
Users are presented with digests of the directory as it evolves over time and can verify someone's \pk against a digest of the directory, preventing equivocation with respect to that digest.
The remaining problem for key transparency schemes is to prevent equivocation about the digests themselves.
For this, current schemes rely on federated trust\cite{coniks}, any-trust assumptions\cite{arpki}, non-collusion between actors\cite{arpki, aki} or on users gossiping between themselves\cite{ctgossip,ect,coniks,dtki} or with trusted validators\cite{aki}.

With \Sys, we propose using the Bitcoin blockchain as a hard-to-coerce, trustworthy witness that can vouch for directory digests.
For example, in Certificate Transparency (CT), a log server would directly witness \emph{signed tree heads} (STHs) in Bitcoin via a \Sys log.
Users can efficiently look up new STHs in the \Sys log and be certain that the log server has not equivocated about them.
We believe this approach could be more resilient to attacks, as a compromised log server cannot equivocate without forking the Bitcoin blockchain.
Also, because most transparency schemes publish digests of the directory periodically, we believe they are amenable to being secured by \Sys.

\subsubsection{Blockchain-based Transparency}
\label{sec:background:motivation:blockchain-transparency}
Blockchain-based transparency schemes\cite{keybase,blockstack} are promising due to their simplicity and resilience to forks, but the overhead of downloading all blockchain data makes them unusable on many devices.
\Sys can decrease the overhead of these schemes from currently \blockchainsize\cite{bitcoin-size} to around \headerssize.
For example, \Sys can enable thin clients running on mobile phones to efficiently audit the Bitcoin-witnessed Keybase \pkd\cite{keybase}.
Currently, Keybase publishes digests of their \pkd in Bitcoin by creating transactions signed by a predetermined \pk\cite{keybase-scheme}.
Keybase clients recognize these transactions and read directory digests from them (see \secref{sec:related-work} for details).
The problem with this approach is that thin clients cannot securely use Bloom filtering (see \secref{sec:background:bitcoin:thin}) to avoid downloading irrelevant transactions, as an adversary could selectively hide Keybase transactions and equivocate about the directory (we explain this attack in \secref{sec:catena:design:auditing}).
\Sys prevents this attack and also has the advantage of not polluting Bitcoin's unspent transaction output (UTXO) set\cite{keybase-opret}.

\Sys can also be used to improve Blockstack's thin client security \cite{blockstack}.
Currently, to benefit from Bitcoin's resilience against forks, Blockstack clients need to download the entire blockchain and compute their own \emph{consensus hash} over all Blockstack-related operations (see \secref{sec:related-work} for details).
Blockstack clients could also choose to trust someone else's consensus hash and verify \pk lookups against it efficiently using Simplified Name Verification (SNV)\cite{blockstack}.
However, clients still have to download full Bitcoin blocks to update that consensus hash or continue trusting someone else to update it.
As with Keybase, Bloom filtering cannot be used securely to filter Blockstack transactions.
To fix this problem, we propose using a \Sys log to keep track of Blockstack operations rather than scattering them through the blockchain.
In this way, thin clients can efficiently download just the Blockstack operations and quickly compute their own consensus hashes.

One disadvantage of this approach, according to one of the Blockstack co-founders\cite{blockstack-shea-jun-2016}, is that it requires a secret key to manage the \Sys log and would thus ``centralize'' the system.
To address this, an alternative design would be to introduce \emph{auditors} who verify and publish Blockstack consensus hashes in a jointly-signed \Sys log.
While this approach centralizes trust for thin clients, such as mobile phones, it does so in a more accountable and transparent manner.
Specifically, the auditors can't equivocate about consensus hashes but can still publish \emph{internally inconsistent}\cite{ht} consensus hashes (see \secref{sec:discussion:agnostic}).
However, such misbehavior would be evident in the Bitcoin blockchain when audited by a full Blockstack client.

\subsubsection{Software Transparency}
\Sys can prevent equivocation in \emph{software transparency} schemes\cite{software-transparency} and thus thwart man-in-the-middle attacks that try to inject malicious software binaries on victims' machines\cite{software-transparency}.
In fact, Bitcoin developers were concerned in the past about these kinds of attacks on Bitcoin binaries\cite{bitcoin-binary-transparency}.
To prevent these attacks, software vendors can publish digests of new versions of their software in a \Sys log.
Customers can then verify any version downloaded from a vendor's website against the vendor's log.
Previous work\cite{cosi} already highlights the necessity of software transparency in the face of insecure software update schemes\cite{secure-software-updates,attacks-on-package-managers}, key loss or compromise \cite{microsoft-golden-key} and black markets for code-signing certificates\cite{blackmarket-certs}.

\subsubsection{Tor Directory Servers}
\Sys can be used to prevent Tor directory servers\cite{tor} from equivocating about the directory of Tor relays.
Equivocation attacks are particularly concerning for Tor because they enable an attacker to easily deanonymize users by pointing them towards attacker-controlled Tor relays.
In fact, Tor Transparency\cite{tortransparency} plans to address these attacks by publicly logging the Tor directory consensus.
In the same spirit, we propose using \Sys to increase the resilience of Tor Transparency.
With \Sys, directory servers can publish the consensus in a \Sys log by jointly signing it using a Bitcoin multisignature\cite{multisig}.
Since Tor does not try to conceal who is connected to the network\cite{tor}, we are not concerned about \Sys's header relay network learning who is using Tor.
% If Tor users want to hide that they use Tor, they can rely on Tor bridges.
Finally, because Tor consensus is updated every hour, we believe it should be suitable for embedding in a \Sys log.

\subsubsection{Consensus Amongst $n$ Servers}
\Sys can be used by a set of $n$ servers to reach consensus on a log of operations, where each server manages its own secret key and does not necessarily trust the other $n-1$ servers.
In this scheme, each server submits an operation to the log by creating a \Sys transaction that is spendable by all $n$ servers (see \secref{sec:model:actors:log-server}).
To disincentivize the other servers from stealing the coins, the log is funded with small amounts of bitcoins and is frequently ``re-funded'' (see \secref{sec:catena:design:refund}).
This scheme allows all servers to reach consensus on the log and relies on Bitcoin miners to decide which server's operation gets included in the log.
To prevent adversarial servers from monopolizing the log with their operations by paying higher transaction fees, the servers can agree on an upper bound on fees.

%\subsubsection{Integrity-sensitive Systems}
%Verena, SUNDR\cite{sundrosdi}, SPORC. SPORC/SUNDR assume clients know each other's public keys (e.g., PKI) => clients can gossip securely and detect equivocation.

\input{chap2-bkg-bitcoin}